PeerMind

### 2016-08-06 paper.tex
TODOs.

@@

>>>>

\todo[inline]{Do we take into the account the distribution of votes? So if you have a very large standard deviation
we might want to prefer a decision less than some other decision with smaller standard deviation, but maybe
also smaller (but still positive) average. Is distribution of votes influencing dynamic quorum?}

@@

\todo[inline]{Or should we be normalizing? In a way we should not normalize if votes are discarded because
member explicitly delegated so ($M_3$ above), but if votes are discarded because we could not compute
all delegations, we might want to automatically normalize.}
